\documentclass[11pt]{res} % default is 10 pt
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\newcommand\textbox[1]{%
  \parbox{.333\textwidth}{#1}%
}
\setlength{\textheight}{9.5in} % increase text height to fit resume on 1 page
\newsectionwidth{0pt}  % So the text is not indented under section headings

\begin{document} 
 
\name{SAMEER JAGDALE\\[12pt]} % the \\[12pt] adds a blank line after name

%\address{{\bf PRESENT ADDRESS} \\   176 Seventh Avenue \\   Troy, NY
       %  12180   \\ (518) 274-8671}
%\address{{\bf PERMANENT ADDRESS} \\ 9280 Fox Harrow Lane \\ Annandale,
       %  VA 22003 \\ (703) 425-2734}
 
                                             
\begin{resume}
                                               
 
%\section{OBJECTIVE}
 %  A mechanical engineering  position  integrating  automation  into 
%manufacturing. 
 
\section{EDUCATION} 
\begin{itemize}
\item
\noindent McGill University,  \hfill \hfill Montreal, QC\\
\noindent MSc Computer Science, \textbf{G.P.A. 3.86/4.0}  \hfill \hfill September 2012 - Present
\item
\noindent University of Pune,  \hfill \hfill Pune, India\\
\noindent Bachelor of Engineering, \textbf{G.P.A. 3.7/4.0}  \hfill \hfill August 2008 - June 2012
\end{itemize}
\section{EXPERIENCE} 
\noindent \textbf{McGill University} \hfill \hfill Montreal,QC \\
\noindent Teaching Assistant \hfill \hfill January 2013 - Present
\begin{itemize}
\item Courses taught :  Operating Systems and Program Analysis and transformations.
\item Explained key concepts and guided students to appreciate challenges in developing operating systems kernels
optimized for enhanced performance in different computing environments.
\item Helped students simulate fundamental components of operating systems such as file system, inter-process
communication, multi-threading et al.
\end{itemize}

\noindent \textbf{Tata Consultancy Services} \hfill \hfill Pune, India\\
\noindent Project Trainee \hfill \hfill June 2011 - April 2012 \\
\textbf{System to determine plasma temperature using real-time image processing}
\begin{itemize}
\item Developed as part of my senior year project course. The project involved development of a prototype that calculated the
temperature, in real time, of plasma during a nuclear fusion reaction from images captured from a high resolution camera.
\item Developed in C++ and utilized the OpenCV library for the image processing module and the OpenCL framework for GPU
interfacing. GTK2 was used to develop the GUI.
\end{itemize}

\section{TECHNICAL SKILLS} 
\begin{itemize} 
\item Proficient in Java, C, C++ and Matlab.
\item Basic knowledge of shell programming, HTML, Javascript and Python.
\item Courses: Computer Networks, Distributed Systems, Compiler optimisation, Intro to Crowdsourcing.
\end{itemize}
\section{MASTER'S THESIS} 
\noindent \textbf{Sable Research Lab},McGill University  \hfill \hfill Montreal,QC\\
\noindent Research Assistant \hfill \hfill May 2013- Present\\
Advisor : Prof. Laurie Hendren. \\
\textbf{VeloCty}
\begin{itemize}
\item Extension to the Velociraptor compiler toolkit developed at the Sable Lab. It aims to compile functions written in
high-level array based languages such as Matlab and Python to C++ with OpenMP pragmas. 
\item Functions are packaged as shared libraries that can be called from the source language, allowing users to continue
writing code in their preferred high-level language while compiling specific hot methods to parallel code.
\end{itemize}
\section{HOBBIES} 
 
Volleyball, weightlifting, and automotive repair 
 

\end{resume}
\end{document}











